---
title: "Question set 3"
output:
  pdf_document:
    includes:
      in_header: "preamble.tex"
    toc: true
    pandoc_args: ["--wrap=none"]
author: Deep Hariya, BS2324
---

```{r setup, include=FALSE}
library(reticulate)
library(wrappedtools)
knitr::opts_chunk$set(echo = TRUE)
```

\newpage

# Question 1:

\smallskip

We have a random sample of size $101$ from a $N(\mu, 1)$ population, where $\mu\in\mathbb{R}$ is unknown. We want to estimate $\mu$. There are two contending estimators: the sample mean and the sample median (i.e., the central-most value after you order the random sample). We want to approximate the standard errors of these estimators. Do this using simulation for $\mu = 10$ and $\mu=20$.

\medskip

## Solution:

Here we first generate a random sample of size 101 with *true mean value* $\mu =10$ and $\mu = 20$. Then to compare `mean()` and `median()` we find the standard error of mean and median:

#### Case 1:
When *true mean* is $10$:
```{r}
mu1 = 10
means1 = c()
medians1 = c()
for(i in 1:10000){
  v = rnorm(101, mu1, 1)
  Mn = mean(v)
  Md = median(v)
  X = c(Mn,Md)
  means1 = append(means1, X[1])
  medians1 = append(medians1, X[2])
}
mean_error1 = sd(means1)
median_error1 = sd(medians1)
mean_error1
median_error1
```
We get standard error of mean is `r mean_error1` and the standard error of median is `r median_error1`

\smallskip

#### Case 2:
When *true mean* is $20$:
```{r}
mu2 <- 20
means2 <- c()
medians2 <- c()
for(i in 1:10000){
  k <- rnorm(101, mu2, 1)
  Mn <- mean(k)
  Md <- median(k)
  X <- c(Mn,Md)
  means2 <- append(means2, X[1])
  medians2 <- append(medians2, X[2])
}
mean_error2 <- sd(means2)
median_error2 <- sd(medians2)
print(mean_error2)
print(median_error2)
```
We get standard error of mean is `r mean_error2` and the standard error of median is `r median_error2`

From above experiment we can see that standard error of median is always higher than the standard error of mean. Hence we can conclude that mean is always a better estimator than median.


\newpage

# Question 2:

\smallskip

A point, $P$, is chosen at random on the circumference of the unit circle centered at the origin. All points are equally likely. Let $(X, 0)$ be the point where the tangent hits the x-axis. Take $X = 0$ if the $P$ is at $(0, -1)$ or (0, 1). Use simulation to form an idea about the distribution of $X$. Is the distribution normal? Answer this question by overlaying the best normal PDF on the histogram, and then visually ascertaining the fit.

\medskip


## Solution:

Here we first generate a uniform random sample of $\theta$ from $(0,2\pi)$ and the $X$ is nothing but $\sec(\theta)$, so we make histogrm of $X$.
```{r}
set.seed(34857)
X <- 1/cos(runif(1000000, 0, 2*pi))
hist(X,xlim = c(-30,30), n = 1000000,xlab="",ylab='')
```

This is clearly not a normal distribution, to demonstrate this we can try to fit in a normal distribution. 

```{r}
library(MASS)
X <- 1/cos(runif(10000, 0, 2*pi))
hist(X, n = 10000,prob = T,xlim=c(-40,40),xlab="",ylab='')
fit <- fitdistr(X, "normal")
para <- fit$estimate
curve(dnorm(x, para[1], para[2]), col = 'red', add = TRUE)
legend("topright", legend = "Normal PDF", col = 'red',lwd = 1,lty  = 1)
```

As we can clearly see, our histogram doesnt fit the normal distribution curve, hence this is not a normal distribution


\newpage

# Question 3:

\smallskip

The same set up as above. Find (using simulation) two numbers $L$ and $U$ such that $X$ lies between them with $90\%$ probability. The smaller is $U -L$, the happier I would be. Also find (using simulation) the probability that $X$ exceeds 5.

\medskip

## Solution:

#### Part 1:

\smallskip

Same setup as before, We first get $X$ as $\sec(\theta)$, where $\theta$ is chosen uniformly at random. Here we use `quantile()` function to get values for $U$ and $L$
```{r}
T <- runif(1000000, 0, 2*pi)
X <- 1/cos(T)
U <- quantile(X,0.05)
L <- quantile(X,0.95)
print(c(U,L))
```

And hence you get $U$ = `r U` and $L$ = `r L`

\medskip

#### Part 2:

\smallskip

And to get probability $P(X > 5)$ we can do:

```{r}
T <- runif(1000000, 0, 2*pi)
X <- 1/cos(T)
P <- 100*mean(X>5)
print(P)
```
$\therefore$ we get probability $P=`r P`\%$