---
title: "Assignment 1"
output:
  pdf_document:
    includes:
      in_header: "preamble.tex"
    toc: true
    pandoc_args: ["--wrap=none"]
author: Deep Hariya, BS2324
---

\newpage

# Question 1:

\smallskip

Consider the dataset about Amazon books stored given in the class web- page. Use R to compute the multiple correlation between **Amazon** **Price**

and (**NumPages**, **Height**, **Width** and **Thickness**). You may use direct computation or a package.

\medskip

## Solution:

```{r}
x = read.delim('amazon-books.txt')
x = na.omit(x)
dat = x[,c(3,4,6,10,11,12,13)]
names(dat) = c('lp','ap','page','h','w','t','wt')
tmp = lm(ap~page+h+w+t,data=dat)
sqrt(summary(tmp)$r.sq)
```

\newpage

# Question 2:

\smallskip

Use the same data set once again to compute partial correlation between **List** **Price** and **Amazon Price** given **Weight** and **Thick**. You may use direct computation or a package.

\medskip

## Solution:

```{r}
ap.filtered = lm(ap~w+t,data=dat)$resid
lp.filtered = lm(lp~w+t,data=dat)$resid
cor(ap.filtered, lp.filtered)

```
